### 2011-01-21 paper/approach.tex
More work on Experimental Approach and Learning Methods

>>>>

Given the goal of producing a deterministic, feedforward motion
function $g(t)$, we now turn to several important considerations.  \secref{learningMethods} talks about how this function is generated, \secref{platformDetails} discusses the hardware platform on which it is run, and \secref{fitnessEvaluation} details exactly how its fitness is measured.

### 2011-01-21 paper/learningMethods.tex
More work on Experimental Approach and Learning Methods

\edit{write this.  Old quadratot Method section below}

@@

We use several parameterized motion models that command motors to
positions based on a sine wave, creating a periodic pattern.  While we
investigated several models, for the bulk of our experiments, we used
a model whose five parameters are: amplitude, wavelength, scale inner
vs outer motors, scale left vs right motors, scale back vs front
motors. Each strategy below attempts to choose the best possible
parameters for this motion model.

>>>>

There are a plethora of methods available for the creation of a vector motion generating function $g(t)$, and we've chosen two for comparison in this study.

The first method is to choose a family of \emph{parametrized functions}.  By fixing the parameters to a particular set of values, we obtain a deterministic motion function over time.  We tried several parametrizations on the robot and, obtaining reasonble early success, settled on one particular parametrization.  We dubbed this the \emph{SineModel5}, as it has five parameters and employs a sine wave as its root pattern.

The five parameters are as follows:

 - amp - Amplitude
 - tau   - sine wave period
 - multIO - multiplier scaling inner joings from outer joints
 - multFB - multiplier scaling front joints from back joints
 - multLR - multiplier scaling left joints from right joints
(verify this)

Inuitively, SineModel5 starts with a sine wave of amplitude 1

 used is a function parametrized by five numbers, shown in \figref{foo}

\edit{make figure to go here, show drawing with inner/outer, l/r, and f/b motors.}

\edit{write this.  Old quadratot Method section below alsdkfj }

@@

We use several parametrized motion models that command motors to
positions based on a sine wave, creating a periodic pattern.  While we
investigated several models, for the bulk of our experiments, we used
a model whose five parameters are: amplitude, wavelength, scale inner
vs outer motors, scale left vs right motors, scale back vs front
motors. Each strategy below attempts to choose the best possible
parameters for this motion model.

### 2011-01-21 paper/problemDefinition.tex
More work on Experimental Approach and Learning Methods

\section{Problem definition}
% Precisely define the problem you are addressing (i.e. formally specify
% the inputs and outputs). Elaborate on why this is an interesting and
% important problem.
%
%\edit{write this.  Quadratot report section below}
%
%We are testing several different learning methods to design a
%parametrized gait for a quadruped robot from the Cornell Computational
%Synthesis Lab.
%
%The output each of the learning algorithms is a function of time,
%$f(t)$, that outputs a vector of commanded motor positions.  This
%function is generated using a parametrized motion model, described in
%\secref{implement}.
%
%The robot executes these commands and measures its change in location
%using the tracking system described in \secref{implement}.  The input
%to the learning algorithms is this measured displacement, which the
%algorithms attempt to maximize. This displacement is measured for each
%gait over a constant length run, usually 12 seconds.
%
%A comparison and evaluation of the many different methods available
%for optimizing the gait of legged robots will be useful for future
%work on this challenging multidimensional control problem.

@@

Mathematically, we define a gait as a function that specifies
commanded motor positions for a robot over time.  Using this
definition, we require one function per motor.  We can write gaits
without feedback --- also called feed forward gaits --- as

\be
x_i = f_i(t)
\ee

\noindent for commanded position $x_i$ for motor $i$.  The
function depends only on time.  Using the same framework, a gait
including measured motor position, force, or other values could be
written as

\be
x_i = f_i(t, z)
\ee

\noindent for some measurement $z$.  Though perhaps obvious, it is
worth noting that feedforward gaits are deterministic (unless they
include random elements), producing the same command pattern each time
they are run.  The output of a gait that includes feedback, on the
other hand, depends on the actual measurements, and noise in these
measurements may result in different $x_i$ values each time they are
run.

>>>>

\section{Problem definition}
% Precisely define the problem you are addressing (i.e. formally specify
% the inputs and outputs). Elaborate on why this is an interesting and
% important problem.
%
%\edit{write this.  Quadratot report section below}
%
%We are testing several different learning methods to design a
%parametrized gait for a quadruped robot from the Cornell Computational
%Synthesis Lab.
%
%The output each of the learning algorithms is a function of time,
%$g(t)$, that outputs a vector of commanded motor positions.  This
%function is generated using a parametrized motion model, described in
%\secref{implement}.
%
%The robot executes these commands and measures its change in location
%using the tracking system described in \secref{implement}.  The input
%to the learning algorithms is this measured displacement, which the
%algorithms attempt to maximize. This displacement is measured for each
%gait over a constant length run, usually 12 seconds.
%
%A comparison and evaluation of the many different methods available
%for optimizing the gait of legged robots will be useful for future
%work on this challenging multidimensional control problem.

@@

Mathematically, we define a gait as a function that specifies
a vector of commanded motor positions for a robot over time.
%Using this definition, we require one function per motor.
We can write gaits without feedback --- also called feed forward gaits
--- as

\be
\vec{x} = g(t)
\ee

%\noindent for commanded position $x_i$ for motor $i$.  The
\noindent for commanded position vector $\vec{x}$.  The
function depends only on time.  Using the same framework, a gait
including measured motor position, force, or other values could be
written as

\be
\vec{x} = g(t, \vec{z})
\ee

\noindent for some measurement vector $\vec{z}$.  Though perhaps obvious, it
is worth noting that feedforward gaits are deterministic (unless they
include random elements), producing the same command pattern each time
they are run.  The output of a gait that includes feedback, on the
other hand, depends on the actual measurements, and noise in these
measurements may result in different $\vec{x}$ values each time they are
run.
